\textbf{quicR}:\ An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays

### 2025-05-21 man/manuscript/softwareX_submission.tex
Edited the comparisons table.

            \begin{table}[ht]
                \centering
                \begin{tblr}{
                    cells     = {font = \fontsize{11pt}{11pt}\selectfont},
                    colspec   = {rcc}, 
                    row{1}    = {font=\bfseries},
                    rowhead   = 1,
                    width     = \textwidth
                }
                    \hline
                    \SetCell[c=1]{c}Feature / Benchmark & \textbf{quicR} & \textbf{QuICSeedR} \\ 
                    \hline
                    Number of input files required & 1 & 2 \\ 
                    Number of threshold methods & 2 & 3 \\
                    Requires manual metadata entry & No & Yes \\
                    Actively maintained & Yes & No \\
                    Built-in bulk analysis support & No & Yes \\
                    Diagnostic analysis functionality & No & Yes \\
                    Incorporates dilution factors & Yes & No \\
                    Converts time units & No & Yes \\
                    Calculates individual metrics independently & Yes & No \\
                    \hline
                    Plate view plot execution time (s) & 0.0978 & 0.0616 \\
                    Metric plot execution time (s) & 0.0108 & 0.0052 \\
                    Metric calculations (MPR, MS, etc.) (s) & 0.3912 & 0.0184 \\
                    Metadata parsing time (s) & 0.1376 & 0.0374 \\
                    Raw data parsing time (s) & 0.0722 & 0.0498 \\
                    Bulk analysis (6 files) (s) & 10.9738 & 0.8486 \\
                    \hline
                \end{tblr}
                \caption{Comparison of core features and execution times between \textbf{quicR} and \textbf{QuICSeedR}. While \textbf{QuICSeedR} demonstrates superior execution speed, \textbf{quicR} offers enhanced metadata handling, metric flexibility, and support for unprocessed instrument output files. All benchmarks were performed using the same dataset and machine (Windows 11, 16GB RAM).}
                \label{tbl:benchmark}
            \end{table}

>>>>

            \begin{table}[ht]
                \centering
                \begin{tblr}{
                    cells     = {font = \fontsize{11pt}{11pt}\selectfont},
                    colspec   = {rcc}, 
                    row{1}    = {font=\bfseries},
                    rowhead   = 1,
                    width     = \textwidth
                }
                    \hline
                    \SetCell[c=1]{c}Feature / Benchmark & \textbf{quicR} & \textbf{QuICSeedR} \\ 
                    \hline
                    Number of input files required & 1 & 2 \\ 
                    Number of threshold methods & 2 & 3 \\
                    Automated metadata entry & Yes & No \\
                    Actively maintained & Yes & No \\
                    Built-in bulk analysis support & No & Yes \\
                    Diagnostic analysis functionality & No & Yes \\
                    Incorporates dilution factors & Yes & No \\
                    Converts time units & No & Yes \\
                    Calculates metrics independently & Yes & No \\
                    \hline
                    Plate view plot execution time (s) & 0.0978 & 0.0616 \\
                    Metric plot execution time (s) & 0.0108 & 0.0052 \\
                    Metric calculations (MPR, MS, etc.) (s) & 0.3912 & 0.0184 \\
                    Metadata parsing time (s) & 0.1376 & 0.0374 \\
                    Raw data parsing time (s) & 0.0722 & 0.0498 \\
                    Bulk analysis (6 files) (s) & 10.9738 & 0.8486 \\
                    \hline
                \end{tblr}
                \caption{Comparison of core features and execution times between \textbf{quicR} and \textbf{QuICSeedR}. While \textbf{QuICSeedR} demonstrates superior execution speed, \textbf{quicR} offers enhanced metadata handling, metric flexibility, and support for unprocessed instrument output files. All benchmarks were performed using the same dataset and machine (Windows 11, 16GB RAM).}
                \label{tbl:benchmark}
            \end{table}
